---
title: "3_Statistical_analyses"
author: "Lucas Sire"
date: "4/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

##  General information

This R Markdown file is attached to the article *"Sire et al. 2021 - Insects Facing Forest Dieback—Catastrophe or Part of Natural Succession Dynamics?"*.

It corresponds to the R script that generated results discussed in the paper.

All files (Raw and complementary files) attached to this study and necessary to redo the following analyses are publicly available in the GitHub repository: *https://github.com/Lucasire/Malaise_FR_2017*.

## Background

The analyses are done on data coming from 56 plots among two regions in France. Sampling period was carried out from May to September 2017 using Malaise traps sampled every month. Along insect sampling, all environmental data for each **natural plot** were assessed by forest experts. (No experimental plot was designed and altered on purpose).

Samples were treated with **metabarcoding approach**.

## Libraries

```{r Libraries}
library(car)
library(performance)
library(see)
library(multcomp)
library(here)
library(mvabund)
library(ordinal)
library(ecoCopula)
library(tidyr)
library(dplyr)
library(labdsv)
library(corrplot)
library(ggplot2)
library(ggrepel)
library(RColorBrewer)
library(tidygraph)
library(ggraph)
library(glm2)
library(ggrepel)
library(lattice)
library(gridExtra)
library(indicspecies)
library(phyloseq)
library(dichromat)
library(vegan)
library(phyloseq)
library(phangorn)
library(seqinr)
library(ape)
library(tcltk)
library(iNEXT)
library(vegan)
```

### Extrapolations of species diversity

```{r Extrapolations, echo=TRUE, message=FALSE, warning=FALSE}
### Data importation

OTUs_list <- read.table("OTUs.txt", h = T)

Col_list <- read.table("Col.txt", h = T)

Dip_list <- read.table("Dip.txt", h = T)

Hem_list <- read.table("Hem.txt", h = T)

Hym_list <- read.table("Hym.txt", h = T)

Lep_list <- read.table("Lep.txt", h = T)

Others_list <- read.table("Others.txt", h = T)

OTUs_specpool <- read.table("OTUs_specpool.txt", h = T)

Months <- read.table("Months.txt", h = T)

# Accumulation curves

### Grouping


Total <- rowSums(OTUs_list)
May <- rowSums(OTUs_list[,159:211])
June <- rowSums(OTUs_list[,105:158])
July <- rowSums(OTUs_list[,51:104])
August <- rowSums(OTUs_list[,1:50])
TOTAL <- cbind(May, June, July, August, Total)

Col_Tot <- rowSums(Col_list)
Dip_Tot <- rowSums(Dip_list)
Hem_Tot <- rowSums(Hem_list)
Hym_Tot <- rowSums(Hym_list)
Lep_Tot <- rowSums(Lep_list)
Others_Tot <- rowSums(Others_list)


### Hill Numbers


xOTUs <- iNEXT(Total, q = 0, datatype = "incidence_freq")
xMay <- iNEXT(May, q = 0, datatype = "incidence_freq")
xJune <- iNEXT(June, q = 0, datatype = "incidence_freq")
xJuly <- iNEXT(July, q = 0, datatype = "incidence_freq")
xAugust <- iNEXT(August, q = 0, datatype = "incidence_freq")
xTOTAL <- iNEXT(TOTAL, q = 0, datatype = "incidence_freq")

xCol <- iNEXT(Col_Tot, q = 0, datatype = "incidence_freq")
xDip <- iNEXT(Dip_Tot, q = 0, datatype = "incidence_freq")
xHem <- iNEXT(Hem_Tot, q = 0, datatype = "incidence_freq")
xHym <- iNEXT(Hym_Tot, q = 0, datatype = "incidence_freq")
xLep <- iNEXT(Lep_Tot, q = 0, datatype = "incidence_freq")
xOthers <- iNEXT(Others_Tot, q = 0, datatype = "incidence_freq")


### Extrapolations


specpool(t(OTUs_specpool), t(Months))
specpool(t(OTUs_specpool))


### Figures


pdf(file="Figure 1A-C.pdf")

plot_window <- rbind(c(1,1), c(2,3))
print(plot_window)

layout(plot_window)
par(mar = c(5,5,3,2), cex.axis = 1.5, cex.lab = 1.5, cex.main = 2.5)

for(i in 1:3) {
  plot(xTOTAL, type = 1, show.main = F, show.legend = F, main = "A", col = c("slateblue2", "mediumturquoise", "goldenrod2", "darksalmon", "forestgreen"))
  legend("bottomright", legend = c("Total","May","June", "July", "August"),  col = c("forestgreen", "darksalmon", "goldenrod2", "mediumturquoise", "slateblue2"), lty = 1, lwd = 2, bty = "n", pt.cex = c(1.4,1.4,1.7,1.4), seg.len = 2, cex = 1.5, xjust = 0.9)
  plot(xTOTAL, type = 2, show.main = F, show.legend = F, main = "B", col = c("slateblue2", "mediumturquoise", "goldenrod2", "darksalmon", "forestgreen"))
  plot(xTOTAL, type = 3, show.main = F, show.legend = F, main = "C", col = c("slateblue2", "mediumturquoise", "goldenrod2", "darksalmon", "forestgreen"))
  plot
  }

dev.off()

###

pdf(file="Figure 2.pdf")

colgrad <- (c("cornflowerblue", "tomato2", "yellowgreen", "tan3", "lightgoldenrod2", "lightpink2"))
plot_window <- rbind(c(1,1,1), c(1,1,1), c(2,3,4), c(5,6,7))
print(plot_window)

layout(plot_window)
par(mar = c(2.5,2.5,2.5,2.5), cex.axis = 1.5, cex.lab = 1.5, cex.main = 2.5)
for(i in 1:5) {
  pie(Pie_Chart[,2], main = 'A', labels = c("1295 - 43%", "893 - 30%", "385 - 13%", "218 - 7.3%", "94 - 3.2%", "87 - 2.9%"), cex = 2, edges = 1000, radius = 0.8, clockwise = FALSE, col = colgrad)
  legend("bottomleft", legend = c("Diptera","Hymenoptera","Lepidoptera", "Coleoptera", "Hemiptera", "Others"),  col = colgrad, lty = 1, lwd = 4, bty = "n", pt.cex = c(1.4,1.4,1.7,1.4), seg.len = 2, cex = 1.5, xjust = 0.9)
    plot(xDip, type = 1, show.main = F, show.legend = F, col = c("cornflowerblue"))
    plot(xHym, type = 1, show.main = F, show.legend = F, main = "B", col = c("tomato2"))
    plot(xLep, type = 1, show.main = F, show.legend = F, col = c("yellowgreen"))
    plot(xCol, type = 1, show.main = F, show.legend = F, col = c("tan3"))
    plot(xHem, type = 1, show.main = F, show.legend = F, col = c("lightgoldenrod2"))
    plot(xOthers, type = 1, show.main = F, show.legend = F, col = c("lightpink2"))
}

dev.off()

###

pdf(file="Supplementary Figure 1.pdf")

layout(1)
par(mai=c(1, 1.5, 1, 1))
matrice <- matrix(c(2972, 4071.459, 3963.28))
barplot(matrice
        ,space = 0.5
        ,beside = TRUE
        ,horiz = FALSE
        ,legend.text = FALSE
        ,xlab=""
        ,ylab="MOTUs richness"
        ,cex.lab=2
        ,cex.axis = 1.5
        ,xlim=c(0,5)
        ,ylim=c(0,5000)
        ,lwd = 2
        ,pch=16
        ,col= c("forestgreen", "grey75", "grey42"))
axis(side=1.5,at=c(1,2.5,4),labels=c("OBSERVED","CHAO2","JACK1"),tick=FALSE,cex.axis=1.3)
abline(h = 0, col = "black", lwd = 4)

arrows(2.5, 4072.4599 - 92.98576, 2.5, 4072.459 + 92.98576, col = "black", angle = 90, code = 3, length = 0.3, lwd = 1)
arrows(4, 3964.28 - 81.55737, 4, 3964.28 + 81.55737, col = "black", angle = 90, code = 3, length = 0.3, lwd = 1)

dev.off()
```

## Species Richness

```{r Species richness, echo=FALSE}
### Data import

Pyr_SR = read.csv2("SP_richness.csv")

### Data handling

richness <- (Pyr_SR$SR_Coleoptera) # Change according to what is being tested
dieback <- as.factor(Pyr_SR$classe_depe)
salvage <- as.factor(Pyr_SR$Type)
district <- as.factor(Pyr_SR$site)
my_data <- data.frame(richness, dieback, salvage, district)
str(my_data)

### Run models

# run a GLM
# using poisson (or quasipoisson if dispersion is high)

m1 <- glm(richness ~ dieback * salvage + district, family = poisson)
m2 <- glm(richness ~ dieback * salvage + district, family = quasipoisson)

### Check models and choose the 'best' one

check_model(m1)
check_model(m2)

### Results

Anova(m2)

### Simplification if interaction is not significant

m2_reduced <- glm(richness ~ dieback + salvage + district, family = quasipoisson)
check_model(m2_reduced)
Anova(m2_reduced)

### Tukey posthoc when significant to check which pairs are different, from the overall model

summary(glht(m2_reduced, linfct=mcp(dieback="Tukey")))
```

## Community composition

```{r mvabund and EcoCopula, echo=FALSE}
### Data import and Data handling

X <- read.csv2("X.csv")

Total <- read.csv2("Tot.csv")
Tot <- Total[,5:2976]
Tot <- pmin(as.matrix(Tot),1)

Coleoptera = read.csv2("Col.csv")
Col <- Coleoptera[,5:222]
Col <- pmin(as.matrix(Col),1)

Diptera = read.csv2("Dip.csv")
Dip <- Diptera[,5:1299]
Dip <- pmin(as.matrix(Dip),1)

Hemiptera = read.csv2("Hem.csv")
Hem <- Hemiptera[,5:98]
Hem <- pmin(as.matrix(Hem),1)

Hymenoptera = read.csv2("Hym.csv")
Hym <- Hymenoptera[,5:897]
Hym <- pmin(as.matrix(Hym),1)

Lepidoptera = read.csv2("Lep.csv")
Lep <- Lepidoptera[,5:389]
Lep <- pmin(as.matrix(Lep),1)

Floricolous = read.csv2("Flo.csv")
Flo <- Floricolous[,5:997]
Flo <- pmin(as.matrix(Flo),1)

Non_Floricolous = read.csv2("Non_Flo.csv")
Non_Flo <- Non_Floricolous[,5:1512]
Non_Flo <- pmin(as.matrix(Non_Flo),1)

Parasitoids = read.csv2("Par.csv")
Par <- Parasitoids[,5:717]
Par <- pmin(as.matrix(Par),1)

Non_Parasitoids = read.csv2("Non_Par.csv")
Non_Par <- Non_Parasitoids[,5:1792]
Non_Par <- pmin(as.matrix(Non_Par),1)

### Run models

#########
#  Tot  #
#########


### correlations between sites

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Tot_Corrplot_Site.pdf")
corrplot(cor(t(Tot)), diag = FALSE, tl.cex = 0.3)
dev.off()

### Mvabund object

Tot_mvabund = mvabund(Tot)

Mod_Tot <- manyglm(Tot_mvabund ~ X$Dieback + X$Type + X$District, family="binomial")

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Tot_Mod.pdf")
plot(Mod_Tot)
dev.off()

Mod_Tot2 <- manyglm(Tot_mvabund ~ X$Dieback + X$Type + X$District, family=binomial("cloglog"))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Tot_Mod_2.pdf")
plot(Mod_Tot2)
dev.off()

#### Run 10 times to get a range of p-values

anova = anova(Mod_Tot2)
anova

Mod_Tot2.p.Dieback <- c(0.002, 0.007, 0.004, 0.001, 0.006, 0.004, 0.003, 0.004, 0.006, 0.003)
Mod_Tot2.p.Type <- c(0.053, 0.062, 0.051, 0.051, 0.05, 0.056, 0.057, 0.05, 0.051, 0.049)
Mod_Tot2.p.District <- c(0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001)

Mod_Tot2.p.adjust.Dieback <- p.adjust(Mod_Tot2.p.Dieback, method = "holm", n = length(Mod_Tot2.p.Dieback))
Mod_Tot2.p.adjust.Type <- p.adjust(Mod_Tot2.p.Type, method = "holm", n = length(Mod_Tot2.p.Type))
Mod_Tot2.p.adjust.District <- p.adjust(Mod_Tot2.p.District, method = "holm", n = length(Mod_Tot2.p.District))

Mod_Tot2.p.adjust.Dieback
Mod_Tot2.p.adjust.Type
Mod_Tot2.p.adjust.District

### Ordination

Ord_Tot <- cord(Mod_Tot2)

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Tot_Ord_Raw.pdf")
plot(Ord_Tot, biplot = TRUE)
dev.off()

Tot_Site_Res <- data.frame(Ord_Tot$scores, X)
Tot_Sp_Res <- data.frame(Ord_Tot$loadings, OTUs = colnames(Tot))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Tot_Ord_Environment.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Tot_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = Type, fill = Dieback, color = Dieback), data = Tot_Site_Res, size = 3) +
  scale_fill_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_color_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_shape_manual(values=c(21, 22, 23)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Tot_Site_Res, size = 2) + 
  theme_classic()
dev.off()

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Tot_Ord_District.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Tot_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = District, fill = District, color = District), data = Tot_Site_Res, size = 3) +
  scale_fill_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_color_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_shape_manual(values=c(24, 25)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Tot_Site_Res, size = 2) + 
  theme_classic()
dev.off()


#########
#  Col  #
#########


### correlations between sites

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Col_Corrplot_Site.pdf")
corrplot(cor(t(Col)), diag = FALSE, tl.cex = 0.3)
dev.off()

### Mvabund object

Col_mvabund = mvabund(Col)

Mod_Col <- manyglm(Col_mvabund ~ X$Dieback + X$Type + X$District, family="binomial")

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Col_Mod.pdf")
plot(Mod_Col)
dev.off()

Mod_Col2 <- manyglm(Col_mvabund ~ X$Dieback + X$Type + X$District, family=binomial("cloglog"))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Col_Mod_2.pdf")
plot(Mod_Col2)
dev.off()

#### Run 10 times to get a range of p-values

anova = anova(Mod_Col2)
anova

Mod_Col2.p.Dieback <- c(0.034, 0.038, 0.037, 0.024, 0.040, 0.039, 0.032, 0.031, 0.043, 0.030)
Mod_Col2.p.Type <- c(0.210, 0.182, 0.183, 0.182, 0.176, 0.202, 0.163, 0.199, 0.167, 0.164)
Mod_Col2.p.District <- c(0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001)

Mod_Col2.p.adjust.Dieback <- p.adjust(Mod_Col2.p.Dieback, method = "holm", n = length(Mod_Col2.p.Dieback))
Mod_Col2.p.adjust.Type <- p.adjust(Mod_Col2.p.Type, method = "holm", n = length(Mod_Col2.p.Type))
Mod_Col2.p.adjust.District <- p.adjust(Mod_Col2.p.District, method = "holm", n = length(Mod_Col2.p.District))

Mod_Col2.p.adjust.Dieback
Mod_Col2.p.adjust.Type
Mod_Col2.p.adjust.District

### Ordination

Ord_Col <- cord(Mod_Col2)

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Col_Ord_Raw.pdf")
plot(Ord_Col, biplot = TRUE)
dev.off()

Col_Site_Res <- data.frame(Ord_Col$scores, X)
Col_Sp_Res <- data.frame(Ord_Col$loadings, OTUs = colnames(Col))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Col_Ord_Environment.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Col_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = Type, fill = Dieback, color = Dieback), data = Col_Site_Res, size = 3) +
  scale_fill_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_color_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_shape_manual(values=c(21, 22, 23)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Col_Site_Res, size = 2) + 
  theme_classic()
dev.off()

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Col_Ord_District.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Col_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = District, fill = District, color = District), data = Col_Site_Res, size = 3) +
  scale_fill_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_color_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_shape_manual(values=c(24, 25)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Col_Site_Res, size = 2) + 
  theme_classic()
dev.off()


#########
#  Dip  #
#########


### correlations between sites

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Dip_Corrplot_Site.pdf")
corrplot(cor(t(Dip)), diag = FALSE, tl.cex = 0.3)
dev.off()

### Mvabund object

Dip_mvabund = mvabund(Dip)

Mod_Dip <- manyglm(Dip_mvabund ~ X$Dieback + X$Type + X$District, family="binomial")

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Dip_Mod.pdf")
plot(Mod_Dip)
dev.off()

Mod_Dip2 <- manyglm(Dip_mvabund ~ X$Dieback + X$Type + X$District, family=binomial("cloglog"))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Dip_Mod_2.pdf")
plot(Mod_Dip2)
dev.off()

#### Run 10 times to get a range of p-values

anova = anova(Mod_Dip2)
anova

Mod_Dip2.p.Dieback <- c(0.002, 0.004, 0.002, 0.005, 0.004, 0.004, 0.004, 0.004, 0.005, 0.003)
Mod_Dip2.p.Type <- c(0.149, 118, 0.134, 0.109, 0.127, 0.123, 0.126, 0.118, 0.132, 0.147)
Mod_Dip2.p.District <- c(0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001)

Mod_Dip2.p.adjust.Dieback <- p.adjust(Mod_Dip2.p.Dieback, method = "holm", n = length(Mod_Dip2.p.Dieback))
Mod_Dip2.p.adjust.Type <- p.adjust(Mod_Dip2.p.Type, method = "holm", n = length(Mod_Dip2.p.Type))
Mod_Dip2.p.adjust.District <- p.adjust(Mod_Dip2.p.District, method = "holm", n = length(Mod_Dip2.p.District))

Mod_Dip2.p.adjust.Dieback
Mod_Dip2.p.adjust.Type
Mod_Dip2.p.adjust.District

### Ordination

Ord_Dip <- cord(Mod_Dip2)

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Dip_Ord_Raw.pdf")
plot(Ord_Dip, biplot = TRUE)
dev.off()

Dip_Site_Res <- data.frame(Ord_Dip$scores, X)
Dip_Sp_Res <- data.frame(Ord_Dip$loadings, OTUs = colnames(Dip))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Dip_Ord_Environment.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Dip_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = Type, fill = Dieback, color = Dieback), data = Dip_Site_Res, size = 3) +
  scale_fill_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_color_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_shape_manual(values=c(21, 22, 23)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Dip_Site_Res, size = 2) + 
  theme_classic()
dev.off()

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Dip_Ord_District.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Dip_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = District, fill = District, color = District), data = Dip_Site_Res, size = 3) +
  scale_fill_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_color_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_shape_manual(values=c(24, 25)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Dip_Site_Res, size = 2) + 
  theme_classic()
dev.off()


#########
#  Hem  #
#########


### correlations between sites

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Hem_Corrplot_Site.pdf")
corrplot(cor((Hem)), diag = FALSE, tl.cex = 0.3)
dev.off()

### Mvabund object

Hem_mvabund = mvabund(Hem)

Mod_Hem <- manyglm(Hem_mvabund ~ X$Dieback + X$Type + X$District, family="binomial")

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Hem_Mod.pdf")
plot(Mod_Hem)
dev.off()

Mod_Hem2 <- manyglm(Hem_mvabund ~ X$Dieback + X$Type + X$District, family=binomial("cloglog"))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Hem_Mod_2.pdf")
plot(Mod_Hem2)
dev.off()

#### Run 10 times to get a range of p-values

anova = anova(Mod_Hem2)
anova

Mod_Hem2.p.Dieback <- c(0.007, 0.004, 0.008, 0.006, 0.007, 0.004, 0.004, 0.007, 0.004, 0.002)
Mod_Hem2.p.Type <- c(0.195, 0.176, 0.2, 0.205, 0.19, 0.184, 0.182, 0.190, 0.192, 0.195)
Mod_Hem2.p.District <- c(0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001)

Mod_Hem2.p.adjust.Dieback <- p.adjust(Mod_Hem2.p.Dieback, method = "holm", n = length(Mod_Hem2.p.Dieback))
Mod_Hem2.p.adjust.Type <- p.adjust(Mod_Hem2.p.Type, method = "holm", n = length(Mod_Hem2.p.Type))
Mod_Hem2.p.adjust.District <- p.adjust(Mod_Hem2.p.District, method = "holm", n = length(Mod_Hem2.p.District))

Mod_Hem2.p.adjust.Dieback
Mod_Hem2.p.adjust.Type
Mod_Hem2.p.adjust.District

### Ordination

Ord_Hem <- cord(Mod_Hem2)

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Hem_Ord_Raw.pdf")
plot(Ord_Hem, biplot = TRUE)
dev.off()

Hem_Site_Res <- data.frame(Ord_Hem$scores, X)
Hem_Sp_Res <- data.frame(Ord_Hem$loadings, OTUs = colnames(Hem))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Hem_Ord_Environment.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Hem_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = Type, fill = Dieback, color = Dieback), data = Hem_Site_Res, size = 3) +
  scale_fill_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_color_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_shape_manual(values=c(21, 22, 23)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Hem_Site_Res, size = 2) + 
  theme_classic()
dev.off()

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Hem_Ord_District.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Hem_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = District, fill = District, color = District), data = Hem_Site_Res, size = 3) +
  scale_fill_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_color_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_shape_manual(values=c(24, 25)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Hem_Site_Res, size = 2) + 
  theme_classic()
dev.off()


#########
#  Hym  #
#########


### correlations between sites

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Hym_Corrplot_Site.pdf")
corrplot(cor(t(Hym)), diag = FALSE, tl.cex = 0.3)
dev.off()

### Mvabund object

Hym_mvabund = mvabund(Hym)

Mod_Hym <- manyglm(Hym_mvabund ~ X$Dieback + X$Type + X$District, family="binomial")

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Hym_Mod.pdf")
plot(Mod_Hym)
dev.off()

Mod_Hym2 <- manyglm(Hym_mvabund ~ X$Dieback + X$Type + X$District, family=binomial("cloglog"))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Hym_Mod_2.pdf")
plot(Mod_Hym2)
dev.off()

#### Run 10 times to get a range of p-values

anova = anova(Mod_Hym2)
anova

Mod_Hym2.p.Dieback <- c(0.005, 0.002, 0.003, 0.007, 0.003, 0.006, 0.006, 0.005, 0.006, 0.001)
Mod_Hym2.p.Type <- c(0.035, 0.033, 0.27, 0.028, 0.031, 0.037, 0.035, 0.039, 0.042, 0.029)
Mod_Hym2.p.District <- c(0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001)

Mod_Hym2.p.adjust.Dieback <- p.adjust(Mod_Hym2.p.Dieback, method = "holm", n = length(Mod_Hym2.p.Dieback))
Mod_Hym2.p.adjust.Type <- p.adjust(Mod_Hym2.p.Type, method = "holm", n = length(Mod_Hym2.p.Type))
Mod_Hym2.p.adjust.District <- p.adjust(Mod_Hym2.p.District, method = "holm", n = length(Mod_Hym2.p.District))

Mod_Hym2.p.adjust.Dieback
Mod_Hym2.p.adjust.Type
Mod_Hym2.p.adjust.District

### Ordination

Ord_Hym <- cord(Mod_Hym2)

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Hym_Ord_Raw.pdf")
plot(Ord_Hym, biplot = TRUE)
dev.off()

Hym_Site_Res <- data.frame(Ord_Hym$scores, X)
Hym_Sp_Res <- data.frame(Ord_Hym$loadings, OTUs = colnames(Hym))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Hym_Ord_Environment.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Hym_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = Type, fill = Dieback, color = Dieback), data = Hym_Site_Res, size = 3) +
  scale_fill_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_color_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_shape_manual(values=c(21, 22, 23)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Hym_Site_Res, size = 2) + 
  theme_classic()
dev.off()

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Hym_Ord_District.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Hym_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = District, fill = District, color = District), data = Hym_Site_Res, size = 3) +
  scale_fill_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_color_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_shape_manual(values=c(24, 25)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Hym_Site_Res, size = 2) + 
  theme_classic()
dev.off()


#########
#  Lep  #
#########


### correlations between sites

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Lep_Corrplot_Site.pdf")
corrplot(cor(t(Lep)), diag = FALSE, tl.cex = 0.3)
dev.off()

### Mvabund object

Lep_mvabund = mvabund(Lep)

Mod_Lep <- manyglm(Lep_mvabund ~ X$Dieback + X$Type + X$District, family="binomial")

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Lep_Mod.pdf")
plot(Mod_Lep)
dev.off()

Mod_Lep2 <- manyglm(Lep_mvabund ~ X$Dieback + X$Type + X$District, family=binomial("cloglog"))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Lep_Mod_2.pdf")
plot(Mod_Lep2)
dev.off()

#### Run 10 times to get a range of p-values

anova = anova(Mod_Lep2)
anova

Mod_Lep2.p.Dieback <- c(0.009, 0.008, 0.011, 0.004, 0.008, 0.011, 0.009, 0.003, 0.010, 0.010)
Mod_Lep2.p.Type <- c(0.021, 0.023, 0.016, 0.024, 0.009, 0.017, 0.024, 0.02, 0.018, 0.025)
Mod_Lep2.p.District <- c(0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001)

Mod_Lep2.p.adjust.Dieback <- p.adjust(Mod_Lep2.p.Dieback, method = "holm", n = length(Mod_Lep2.p.Dieback))
Mod_Lep2.p.adjust.Type <- p.adjust(Mod_Lep2.p.Type, method = "holm", n = length(Mod_Lep2.p.Type))
Mod_Lep2.p.adjust.District <- p.adjust(Mod_Lep2.p.District, method = "holm", n = length(Mod_Lep2.p.District))

Mod_Lep2.p.adjust.Dieback
Mod_Lep2.p.adjust.Type
Mod_Lep2.p.adjust.District

### Ordination

Ord_Lep <- cord(Mod_Lep2)

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Lep_Ord_Raw.pdf")
plot(Ord_Lep, biplot = TRUE)
dev.off()

Lep_Site_Res <- data.frame(Ord_Lep$scores, X)
Lep_Sp_Res <- data.frame(Ord_Lep$loadings, OTUs = colnames(Lep))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Lep_Ord_Environment.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Lep_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = Type, fill = Dieback, color = Dieback), data = Lep_Site_Res, size = 3) +
  scale_fill_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_color_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_shape_manual(values=c(21, 22, 23)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Lep_Site_Res, size = 2) + 
  theme_classic()
dev.off()

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Lep_Ord_District.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Lep_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = District, fill = District, color = District), data = Lep_Site_Res, size = 3) +
  scale_fill_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_color_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_shape_manual(values=c(24, 25)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Lep_Site_Res, size = 2) + 
  theme_classic()
dev.off()


#########
#  Flo  #
#########


### correlations between sites

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Flo_Corrplot_Site.pdf")
corrplot(cor(t(Flo)), diag = FALSE, tl.cex = 0.3)
dev.off()

### Mvabund object

Flo_mvabund = mvabund(Flo)

Mod_Flo <- manyglm(Flo_mvabund ~ X$Dieback + X$Type + X$District, family="binomial")

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Flo_Mod.pdf")
plot(Mod_Flo)
dev.off()

Mod_Flo2 <- manyglm(Flo_mvabund ~ X$Dieback + X$Type + X$District, family=binomial("cloglog"))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Flo_Mod_2.pdf")
plot(Mod_Flo2)
dev.off()

#### Run 10 times to get a range of p-values

anova = anova(Mod_Flo2)
anova

Mod_Flo2.p.Dieback <- c(0.006, 0.003, 0.003, 0.006, 0.004, 0.007, 0.006, 0.006, 0.005, 0.003)
Mod_Flo2.p.Type <- c(0.05, 0.046, 0.04, 0.04, 0.043, 0.045, 0.05, 0.038, 0.056, 0.045)
Mod_Flo2.p.District <- c(0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001)

Mod_Flo2.p.adjust.Dieback <- p.adjust(Mod_Flo2.p.Dieback, method = "holm", n = length(Mod_Flo2.p.Dieback))
Mod_Flo2.p.adjust.Type <- p.adjust(Mod_Flo2.p.Type, method = "holm", n = length(Mod_Flo2.p.Type))
Mod_Flo2.p.adjust.District <- p.adjust(Mod_Flo2.p.District, method = "holm", n = length(Mod_Flo2.p.District))

Mod_Flo2.p.adjust.Dieback
Mod_Flo2.p.adjust.Type
Mod_Flo2.p.adjust.District

### Ordination

Ord_Flo <- cord(Mod_Flo2)

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Flo_Ord_Raw.pdf")
plot(Ord_Flo, biplot = TRUE)
dev.off()

Flo_Site_Res <- data.frame(Ord_Flo$scores, X)
Flo_Sp_Res <- data.frame(Ord_Flo$loadings, OTUs = colnames(Flo))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Flo_Ord_Environment.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Flo_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = Type, fill = Dieback, color = Dieback), data = Flo_Site_Res, size = 3) +
  scale_fill_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_color_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_shape_manual(values=c(21, 22, 23)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Flo_Site_Res, size = 2) + 
  theme_classic()
dev.off()

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Flo_Ord_District.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Flo_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = District, fill = District, color = District), data = Flo_Site_Res, size = 3) +
  scale_fill_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_color_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_shape_manual(values=c(24, 25)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Flo_Site_Res, size = 2) + 
  theme_classic()
dev.off()


#############
#  Non_Flo  #
#############


### correlations between sites

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Non_Flo_Corrplot_Site.pdf")
corrplot(cor(t(Non_Flo)), diag = FALSE, tl.cex = 0.3)
dev.off()

### Mvabund object

Non_Flo_mvabund = mvabund(Non_Flo)

Mod_Non_Flo <- manyglm(Non_Flo_mvabund ~ X$Dieback + X$Type + X$District, family="binomial")

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Non_Flo_Mod.pdf")
plot(Mod_Non_Flo)
dev.off()

Mod_Non_Flo2 <- manyglm(Non_Flo_mvabund ~ X$Dieback + X$Type + X$District, family=binomial("cloglog"))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Non_Flo_Mod_2.pdf")
plot(Mod_Non_Flo2)
dev.off()

#### Run 10 times to get a range of p-values

anova = anova(Mod_Non_Flo2)
anova

Mod_Non_Flo2.p.Dieback <- c(0.004, 0.002, 0.002, 0.002, 0.003, 0.002, 0.003, 0.001, 0.004, 0.001)
Mod_Non_Flo2.p.Type <- c(0.07, 0.069, 0.06, 0.08, 0.073, 0.08, 0.075, 0.067, 0.062, 0.06)
Mod_Non_Flo2.p.District <- c(0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001)

Mod_Non_Flo2.p.adjust.Dieback <- p.adjust(Mod_Non_Flo2.p.Dieback, method = "holm", n = length(Mod_Non_Flo2.p.Dieback))
Mod_Non_Flo2.p.adjust.Type <- p.adjust(Mod_Non_Flo2.p.Type, method = "holm", n = length(Mod_Non_Flo2.p.Type))
Mod_Non_Flo2.p.adjust.District <- p.adjust(Mod_Non_Flo2.p.District, method = "holm", n = length(Mod_Non_Flo2.p.District))

Mod_Non_Flo2.p.adjust.Dieback
Mod_Non_Flo2.p.adjust.Type
Mod_Non_Flo2.p.adjust.District

### Ordination

Ord_Non_Flo <- cord(Mod_Non_Flo2)

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Non_Flo_Ord_Raw.pdf")
plot(Ord_Non_Flo, biplot = TRUE)
dev.off()

Non_Flo_Site_Res <- data.frame(Ord_Non_Flo$scores, X)
Non_Flo_Sp_Res <- data.frame(Ord_Non_Flo$loadings, OTUs = colnames(Non_Flo))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Non_Flo_Ord_Environment.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Non_Flo_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = Type, fill = Dieback, color = Dieback), data = Non_Flo_Site_Res, size = 3) +
  scale_fill_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_color_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_shape_manual(values=c(21, 22, 23)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Non_Flo_Site_Res, size = 2) + 
  theme_classic()
dev.off()

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Non_Flo_Ord_District.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Non_Flo_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = District, fill = District, color = District), data = Non_Flo_Site_Res, size = 3) +
  scale_fill_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_color_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_shape_manual(values=c(24, 25)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Non_Flo_Site_Res, size = 2) + 
  theme_classic()
dev.off()


#########
#  Par  #
#########


### correlations between sites

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Par_Corrplot_Site.pdf")
corrplot(cor(t(Par)), diag = FALSE, tl.cex = 0.3)
dev.off()

### Mvabund object

Par_mvabund = mvabund(Par)

Mod_Par <- manyglm(Par_mvabund ~ X$Dieback + X$Type + X$District, family="binomial")

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Par_Mod.pdf")
plot(Mod_Par)
dev.off()

Mod_Par2 <- manyglm(Par_mvabund ~ X$Dieback + X$Type + X$District, family=binomial("cloglog"))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Par_Mod_2.pdf")
plot(Mod_Par2)
dev.off()

#### Run 10 times to get a range of p-values

anova = anova(Mod_Par2)
anova

Mod_Par2.p.Dieback <- c(0.004, 0.005, 0.007, 0.008, 0.001, 0.002, 0.002, 0.004, 0.004, 0.003)
Mod_Par2.p.Type <- c(0.016, 0.26, 0.028, 0.029, 0.026, 0.026, 0.028, 0.033, 0.024, 0.026)
Mod_Par2.p.District <- c(0.001, 0/001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001)

Mod_Par2.p.adjust.Dieback <- p.adjust(Mod_Par2.p.Dieback, method = "holm", n = length(Mod_Par2.p.Dieback))
Mod_Par2.p.adjust.Type <- p.adjust(Mod_Par2.p.Type, method = "holm", n = length(Mod_Par2.p.Type))
Mod_Par2.p.adjust.District <- p.adjust(Mod_Par2.p.District, method = "holm", n = length(Mod_Par2.p.District))

Mod_Par2.p.adjust.Dieback
Mod_Par2.p.adjust.Type
Mod_Par2.p.adjust.District

### Ordination

Ord_Par <- cord(Mod_Par2)

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Par_Ord_Raw.pdf")
plot(Ord_Par, biplot = TRUE)
dev.off()

Par_Site_Res <- data.frame(Ord_Par$scores, X)
Par_Sp_Res <- data.frame(Ord_Par$loadings, OTUs = colnames(Par))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Par_Ord_Environment.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Par_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = Type, fill = Dieback, color = Dieback), data = Par_Site_Res, size = 3) +
  scale_fill_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_color_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_shape_manual(values=c(21, 22, 23)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Par_Site_Res, size = 2) + 
  theme_classic()
dev.off()

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Par_Ord_District.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Par_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = District, fill = District, color = District), data = Par_Site_Res, size = 3) +
  scale_fill_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_color_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_shape_manual(values=c(24, 25)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Par_Site_Res, size = 2) + 
  theme_classic()
dev.off()


#############
#  Non_Par  #
#############


### correlations between sites

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Non_Par_Corrplot_Site.pdf")
corrplot(cor(t(Non_Par)), diag = FALSE, tl.cex = 0.3)
dev.off()

### Mvabund object

Non_Par_mvabund = mvabund(Non_Par)

Mod_Non_Par <- manyglm(Non_Par_mvabund ~ X$Dieback + X$Type + X$District, family="binomial")

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Non_Par_Mod.pdf")
plot(Mod_Non_Par)
dev.off()

Mod_Non_Par2 <- manyglm(Non_Par_mvabund ~ X$Dieback + X$Type + X$District, family=binomial("cloglog"))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Non_Par_Mod_2.pdf")
plot(Mod_Non_Par2)
dev.off()

#### Run 10 times to get a range of p-values

anova = anova(Mod_Non_Par2)
anova

Mod_Non_Par2.p.Dieback <- c(0.002, 0.005, 0.002, 0.004, 0.004, 0.004, 0.006, 0.002, 0.002, 0.005)
Mod_Non_Par2.p.Type <- c(0.070, 0.079, 0.072, 0.071, 0.074, 0.074, 0.091, 0.063, 0.089, 0.063)
Mod_Non_Par2.p.District <- c(0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001, 0.001)

Mod_Non_Par2.p.adjust.Dieback <- p.adjust(Mod_Non_Par2.p.Dieback, method = "holm", n = length(Mod_Non_Par2.p.Dieback))
Mod_Non_Par2.p.adjust.Type <- p.adjust(Mod_Non_Par2.p.Type, method = "holm", n = length(Mod_Non_Par2.p.Type))
Mod_Non_Par2.p.adjust.District <- p.adjust(Mod_Non_Par2.p.District, method = "holm", n = length(Mod_Non_Par2.p.District))

Mod_Non_Par2.p.adjust.Dieback
Mod_Non_Par2.p.adjust.Type
Mod_Non_Par2.p.adjust.District

### Ordination

Ord_Non_Par <- cord(Mod_Non_Par2)

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Non_Par_Ord_Raw.pdf")
plot(Ord_Non_Par, biplot = TRUE)
dev.off()

Non_Par_Site_Res <- data.frame(Ord_Non_Par$scores, X)
Non_Par_Sp_Res <- data.frame(Ord_Non_Par$loadings, OTUs = colnames(Non_Par))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Non_Par_Ord_Environment.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Non_Par_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = Type, fill = Dieback, color = Dieback), data = Non_Par_Site_Res, size = 3) +
  scale_fill_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_color_manual(values=c("chartreuse3", "darkorange1", "brown3")) +
  scale_shape_manual(values=c(21, 22, 23)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Non_Par_Site_Res, size = 2) + 
  theme_classic()
dev.off()

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Non_Par_Ord_District.pdf")
alpha <- 2.5
ggplot() +
  geom_segment(aes(x = 0, y = 0, xend = Factor1 * alpha * 0.95, yend = Factor2 * alpha * 0.95), data = Non_Par_Sp_Res) +
  geom_point(aes(x = Factor1, y = Factor2, shape = District, fill = District, color = District), data = Non_Par_Site_Res, size = 3) +
  scale_fill_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_color_manual(values=c("cadetblue3", "darkorchid4")) +
  scale_shape_manual(values=c(24, 25)) +
  geom_text_repel(aes(x = Factor1, y = Factor2, label = Plot), data = Non_Par_Site_Res, size = 2) + 
  theme_classic()
dev.off()

```

## Heatmaps

```{r Heatmaps, echo=FALSE}
### Data import and Data handling

otu_Dieback <- read.csv("OTU_Boot_Dieback.csv", sep = ";", h = T, row.names = 1)
head(otu_Dieback)

tax_Dieback <- read.csv("OTU_Boot_Taxo.csv", sep = ";", h = T, row.names = 1)
head(tax_Dieback)

class(otu_Dieback)
otumat_Dieback <- as.matrix(otu_Dieback)
class(tax_Dieback)
taxmat_Dieback <- as.matrix(tax_Dieback)

otu_Site <- read.csv("OTU_Boot_Site.csv", sep = ";", h = T, row.names = 1)
head(otu_Site)

tax_Site <- read.csv("OTU_Boot_Taxo.csv", sep = ";", h = T, row.names = 1)
head(tax_Site)

class(otu_Site)
otumat_Site <- as.matrix(otu_Site)
class(tax_Site)
taxmat_Site <- as.matrix(tax_Site)


### Dieback


otu_Dieback_final = otu_table(otumat_Dieback, taxa_are_rows = TRUE)
tax_Dieback_final = tax_table(taxmat_Dieback)

physeq_Dieback = phyloseq(otu_Dieback_final, tax_Dieback_final)
physeq_Dieback

random_tree_Dieback = rtree(ntaxa(physeq_Dieback), rooted=TRUE, tip.label=taxa_names(physeq_Dieback))
physeq_Dieback_tree <-merge_phyloseq(physeq_Dieback, random_tree_Dieback)

physeq_Dieback_final_2 <- phyloseq(otu_Dieback_final, tax_Dieback_final, random_tree_Dieback)
physeq_Dieback_final_2
identical(physeq_Dieback_tree, physeq_Dieback_final_2)


#plot_tree(physeq_Dieback_final_1, color="sample", label.tips="order", ladderize="left", plot.margin=0.3)
#plot_tree(physeq_Dieback_final_1, color="sample", label.tips="family", ladderize="left", plot.margin=0.3)
#plot_tree(physeq_Dieback_final_1, color="sample", label.tips="taxa_names", ladderize="left", plot.margin=0.3)
#plot_heatmap(physeq_Dieback_final_1, "HMSC", "bray", taxa.label = "order", taxa.order = "family", sample.order = c("Low", "Medium", "High"), low="#000033", high="#FF3300")
#plot_heatmap(physeq_Dieback_final_1, "HMSC", "bray", taxa.label = "family", taxa.order = "family", sample.order = c("Low", "Medium", "High"), low="#000033", high="#FF3300")

physeq_Dieback_ordered <- prune_taxa(names(sort(taxa_sums(physeq_Dieback_tree), TRUE)[1:2972]), physeq_Dieback_tree)
plot_heatmap(physeq_Dieback_ordered, taxa.label = "taxa_names", sample.order = c("Low", "Medium", "High"), low="#000033", high="#FF3300")


### District


otu_Site_final = otu_table(otumat_Site, taxa_are_rows = TRUE)
tax_Site_final = tax_table(taxmat_Site)

physeq_Site = phyloseq(otu_Site_final, tax_Site_final)
physeq_Site

random_tree_Site = rtree(ntaxa(physeq_Site), rooted=TRUE, tip.label=taxa_names(physeq_Site))
physeq_Site_tree <-merge_phyloseq(physeq_Site, random_tree_Site)

physeq_Site_final_2 <- phyloseq(otu_Site_final, tax_Site_final, random_tree_Site)
physeq_Site_final_2
identical(physeq_Site_tree, physeq_Site_final_2)


#plot_tree(physeq_Site_final_1, color="sample", label.tips="order", ladderize="left", plot.margin=0.3)
#plot_tree(physeq_Site_final_1, color="sample", label.tips="family", ladderize="left", plot.margin=0.3)
#plot_tree(physeq_Site_final_1, color="sample", label.tips="taxa_names", ladderize="left", plot.margin=0.3)
#plot_heatmap(physeq_Site_final_1, "HMSC", "bray", taxa.label = "order", taxa.order = "family", sample.order = c("Low", "Medium", "High"), low="#000033", high="#FF3300")
#plot_heatmap(physeq_Site_final_1, "HMSC", "bray", taxa.label = "family", taxa.order = "family", sample.order = c("Low", "Medium", "High"), low="#000033", high="#FF3300")

physeq_Site_ordered <- prune_taxa(names(sort(taxa_sums(physeq_Site_tree), TRUE)[1:2972]), physeq_Site_tree)
plot_heatmap(physeq_Site_ordered, taxa.label = "taxa_names", sample.order = c("Aure", "Sault", "Total"), low="#00180c", high="#FFFF66")
```

## TraitGLM

```{r TraitGLM, echo=FALSE}
### Data import

X = read.csv2("X.csv")

Total <- read.csv2("Tot.csv")
Tot <- Total[,5:2976]
Tot <- pmin(as.matrix(Tot),1)

Tot_Trait <- read.csv2("Tot_Trait.csv", row.names = colnames(Tot))

Functional_Group <- read.csv2("Functional_Group.csv")
Func <- Functional_Group[,5:2509]
Func <- pmin(as.matrix(Func),1)

Func_Trait <- read.csv2("Functional_Group_Trait.csv", row.names = colnames(Func))

###########
#  Total  #
###########

### TraitGLM

Tot_Dieback_4 <- traitglm(Tot, X$Dieback, Tot_Trait, method = "glm1path")
Tot_Dieback_4$fourth
anova(Tot_Dieback_4)

Tot_Type_4 <- traitglm(Tot, X$Type, Tot_Trait, method = "glm1path")
Tot_Type_4$fourth
anova(Tot_Type_4)

### Heatmaps

a1 <- max(abs(Tot_Dieback_4$fourth.corner))
a2 <- max(abs(Tot_Type_4$fourth.corner))
colort <- colorRampPalette(c("blue","white","red"))

Tot_4_graph1 <- levelplot(t(as.matrix(Tot_Dieback_4$fourth.corner)), xlab="Dieback level",
                     ylab= "Groups", col.regions=colort(100), at=seq(-a1, a1, length=100),
                     scales = list( x= list(rot = 45), tck = c(1,0)))


Tot_4_graph2 <- levelplot(t(as.matrix(Tot_Type_4$fourth.corner)), xlab="Forest type",
                     ylab= NULL, col.regions=colort(100), at=seq(-a2, a2, length=100),
                     scales = list(x = list(rot = 45), tck = c(1,0)))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Tot_TraitGLM.pdf")
grid.arrange(Tot_4_graph1, Tot_4_graph2, ncol = 2)
dev.off()

#######################
#  Functional Groups  #
#######################

### TraitGLM

Func_Dieback_4 <- traitglm(Func, X$Dieback, Func_Trait, method = "glm1path")
Func_Dieback_4$fourth
anova(Func_Dieback_4)

Func_Type_4 <- traitglm(Func, X$Type, Func_Trait, method = "glm1path")
Func_Type_4$fourth
anova(Func_Type_4)

### Heatmaps

a1 <- max(abs(Func_Dieback_4$fourth.corner))
a2 <- max(abs(Func_Type_4$fourth.corner))
colort <- colorRampPalette(c("blue","white","red"))

Func_4_graph1 <- levelplot(t(as.matrix(Func_Dieback_4$fourth.corner)), xlab="Dieback level",
                          ylab= "Groups", col.regions=colort(100), at=seq(-a1, a1, length=100),
                          scales = list( x= list(rot = 45), tck = c(1,0)))


Func_4_graph2 <- levelplot(t(as.matrix(Func_Type_4$fourth.corner)), xlab="Forest type",
                          ylab= NULL, col.regions=colort(100), at=seq(-a2, a2, length=100),
                          scales = list(x = list(rot = 45), tck = c(1,0)))

pdf(file = "/usr/home/biopatic/sire/statistics/figures/Func_TraitGLM.pdf")
grid.arrange(Func_4_graph1, Func_4_graph2, ncol = 2)
dev.off()
```

## IndVal

```{r IndVal, echo=FALSE}
### Data import and Data handling

Indic_Low = read.csv2("Indic_Sp_Low.csv")
Indic_Low_Matrix <- as.matrix(Indic_Low)

Indic_Med = read.csv2("Indic_Sp_Medium.csv")
Indic_Med_Matrix <- as.matrix(Indic_Med)

Indic_High = read.csv2("Indic_Sp_High.csv")
Indic_High_Matrix <- as.matrix(Indic_High)


### IndVal


IndVal_dieback <- multipatt(Total[,5:2976], X$Dieback, func="IndVal", duleg=T, control=how(nperm=999))
IndVal_dieback
IndVal <- capture.output(summary(IndVal_dieback, indvalcomp=TRUE))

write.csv(IndVal, file = "indval.csv", row.names = F)

# Values recovered separated manually in 3 different files (Indic_Sp_Low.csv, Indic_Sp_Medium.csv, Indic_Sp_High.csv)


### Run loop changing values for each of the 3 different files, accordingly
for (i in 1:8) {
  p_values <- unlist(as.numeric(Indic_High[i,2:11]))
  indic_high.p.adjust <- p.adjust(p_values, method = "holm", n = 10)
  Indic_High
}
```